Corotating Clumps Around Adolescent Low-Mass Stars: Four Years of TESS

### 2023-07-12 paper/ms.tex
update ms

\usepackage{apjfonts}
\usepackage{url}
\usepackage{hyperref}
\usepackage{natbib}
\usepackage{amsmath,amstext,amssymb}
\usepackage[caption=false]{subfig} % for subfloat
\usepackage{xcolor, fontawesome}
\usepackage{color}

@@

%%%%%%%%%%%%%%%%
% INSTITUTIONS %
%%%%%%%%%%%%%%%%
\newcommand{\caltech}{Department of Astronomy, MC 249-17, California Institute of Technology, Pasadena, CA 91125, USA}
\newcommand{\mitkavli}{MIT Kavli Institute and Department of Physics, 77 Massachusetts Avenue, Cambridge, MA 02139}
\newcommand{\berkeley}{Astronomy Department, University of California, Berkeley, CA 94720, USA}
\newcommand{\princeton}{Department of Astrophysical Sciences, Princeton University, 4 Ivy Lane, Princeton, NJ 08540, USA}

@@

% primary authors
\author{Author list \& order not final!}
\author[0000-0002-0514-5538]{Luke~G.~Bouma}
\altaffiliation{51 Pegasi b Fellow}
\affiliation{\caltech}

@@

% [to be confirmed after these]
\author{Saul~Rappaport}
\affiliation{\mitkavli}

@@

@@

@@

% 250 word max!
\begin{abstract}
  Complex quasiperiodic variables (CQVs) are low-mass
  pre-main-sequence stars with nearly periodic optical modulation.
  The modulation is likely induced by dust or gas clumps in orbit at
  the Keplerian corotation radius.  Here, we report new CQVs
  discovered in TESS data collected between July~2018 and Sep~2022.
  Our search of \nstarssearched\ K- and M-dwarfs with $T$$<$16 and
  $d$$<$150\,pc yielded \ngoods\ high-quality CQVs.  Most of these
  discoveries are new, and they include the brightest
  ($T$$\approx$9.5) and closest ($d$$\approx$20\,pc)
  examples of this class of object known, as well as the most massive
  ($\approx$0.6-0.8\,M$_\odot$).  A few objects are outliers among
  outliers; LP 12-502 for instance shows a ``dip complex'' with a
  period and total duration that are fixed over more than 1{,}000
  cycles, but which in detail exhibits anywhere from four to eight
  local minima per cycle.  LP-502 also displayed distinct superposed
  periods simultaneously, and showed drastic shape changes shortly
  after flares.  Broadly speaking, we find that none of the CQVs
  maintain a fixed light curve shape over timescales of more than a
  few hundred cycles, and we revisit the arguments for why transient
  corotating material is the most viable explanation.  In the future,
  we expect that our sample will facilitate modeling and observational
  efforts aimed at understanding these objects, and connecting them to
  the broader contexts of star, disk, and exoplanet evolution.  For
  instance, if the transiting material is dust, then the rate of dip
  evolution implies that of order an asteroid belt's worth of mass
  passes through these structures over their lifetime of $10^8$ years.
\end{abstract}

@@

\begin{figure*}[!t]
	\begin{center}
		\centering
		\includegraphics[width=\textwidth]{f6.pdf}
		\vspace{-0.45cm}
		\caption{
      {\bf Properties of CQVs from our search}.
      The \ngoods\ bonafide CQVs in Table~\ref{tab:thetable} are 
      the black circles; \nmaybes\ candidate CQVs are gray circles.
      The \nstarssearched\ target stars with 120-second cadence data
      acquired by TESS between July~2018 and Sep~2022 are shown as the shaded background on the top panels,
      where darker regions correspond to a larger relative number of observed stars.
      {\bf lgb todo: P vs color needs Pleiades comparison}
		}
		\label{fig:catalogscatter}
	\end{center}
\end{figure*}

@@

Based on our reading of \citet[][Ch.~8]{1992oasp.book.....G}, it seems
somewhat challenging to get neutral hydrogen to have this type of
chromaticity.  Bound-bound absorption provides opacity only at narrow
resonant lines.  Bound-free absorption can provide
wavelength-dependent opacity, but the absorption coefficients
generally {\it grow} with increasing wavelength, rather than {\it
shrink} as one needs in order to get deeper absorption in the blue
than in the red.  H$^-$  fails as a viable opacity source for the same
reason: its absorption coefficient peaks near 8500\,\AA, and is an
order of magnitude smaller at $\approx$3000\AA.
(\citealt{1992oasp.book.....G}, following \citealt{1979MNRAS.187P..59W}).
Thompson scattering is also ruled out, because it is gray.  Dust, with
its relatively featureless but increasing extinction curve when going
bluer into the optical \citep{1989ApJ...345..245C}, is to our
knowledge the most obvious opacity source.

@@

\begin{enumerate}
	%
  \item CQVs are {\it quasi}periodic.  While the mean periods in our
    sample remain fixed over the baseline of available
    observations, the light curve shapes always evolve over timescales
    of thousands of cycles (Figure~\ref{fig:evoln}).
  %
  \item The same CQV can show dips with similar but clearly
    distinct periods.  LP 12-502, for instance, showed dips with four
    distinct periods within $\pm 0.3\%$ of its fundamental period,
    sometimes simultaneously, and each lasting for up to 50 cycles
    (Figure~\ref{fig:lpriver0}).
  %
    \item CQVs evolve over timescales that are both secular
    ($>$100\,cycles) and impulsive ($<$1 cycle).  ``State-switches''
    can cause dips to collapse instantaneously, and are often (but not
    exclusively) linked with observed optical flares.  Dip growth
    however seems to happen over durations of at least ten cycles, and
    slow dip decay also happens.
  %
    \item The rate of dip evolution can be used to place a model-dependent
    constraint on amount of material that is either being accreted or ejected
    during the state changes (Section~\ref{subsec:massflux}).
    Order of magnitude estimates require at least an asteroid belt's worth
    of dust ($10^{-4}$\,$M_\oplus$) over $10^8$ years, or 100 times more 
    material if the occulting matter is gas.
  %
    \item The CQV phenomenon persists for $\gtrsim$150\,Myr, based on
    the existence of multiple CQVs in AB Dor, the Pleiades, and
    Psc-Eri (Section~\ref{subsec:starprops}).  It may extend to even
    older ages, however the lack of detected CQVs in the Hyades and
    Praesepe suggests that the lifetime of the phenomenon may be
    limited to the first few hundred million years.
	%
    \item The duty cycle for CQVs seems to be $\approx 75$\%, based on
    the fraction of bonafide CQVs that turned on or turned off during
    TESS re-observations, two years after their initial observation.
  %
    \item Observed CQVs span a stellar mass range of 0.1-0.8\,M$_\odot$
    (Section~\ref{subsec:extreme}).
  %
    \item The closest CQVs to the Sun are at distances of 15-20\,pc, and
    the brightest CQVs have $V$$\approx$12 ($J$$\approx$7.5).  This
    conclusion is an extrapolation from the CQV sample derived in this work
    being $\gtrsim$80\% complete within 20\,pc.  Expanding our analysis of
    the TESS data to the full frame images would yield a truly
    volume-limited selection function, and would expand the CQV census
    by about a factor of two within 50\,pc, and by a factor of ten
    within 100\,pc.
\end{enumerate}

@@

\facilities{
 	{\it Astrometry}:
		Gaia \citep{2018A&A...616A...1G,2022arXiv220800211G}.
 	{\it Imaging}:
    Second Generation Digitized Sky Survey. %,
    %SOAR~(HRCam; \citealt{tokovinin_ten_2018}).
		%Keck:II~(NIRC2).
		%Gemini:South~(Zorro; \citealt{scott_nessi_2018}.
		%Gemini:North~(`Alopeke; \citealt{scott_nessi_2018,scott_twin_2021}.
 	{\it Spectroscopy}:
		%CTIO1.5$\,$m~(CHIRON; \citealt{tokovinin_chironfiber_2013}),
		%PFS ({\bf CITE}),
		%Tillinghast:1.5m~(TRES).
		%MPG2.2$\,$m~(FEROS; \citealt{kaufer_commissioning_1999}),
		%AAT~(Veloce; \citealt{gilbert_veloce_2018}).
		%AAT~(HERMES; \citealt{lewis_2002_hermers_2df,sheinis_2015_hermes}),
		Keck:I~(HIRES; \citealt{1994SPIE.2198..362V}).
		%VLT:Kueyen~(FLAMES; \citealt{pasquini_2002}).
 	  %Euler1.2m~(CORALIE),
 	  %ESO:3.6m~(HARPS; \citealt{mayor_setting_2003}).
 	{\it Photometry}:
		%ASTEP:0.40$\,$m (ASTEP400),
		%CTIO:1.0m (Y4KCam),
		%Danish 1.54m Telescope,
		%El Sauce:0.356$\,$m,
		%Elizabeth 1.0m at SAAO,
		%Euler1.2m (EulerCam),
		%Kepler,
		%Magellan:Baade (MagIC),
		%Max Planck:2.2m	(GROND; \citealt{greiner_grond7-channel_2008})
		%MuSCAT3 \citep{Narita_2020},
		%NTT,
		%SOAR (SOI),
 	  TESS \citep{2015JATIS...1a4003R},
		%TRAPPIST \citep{jehin_trappist_2011},
		%VLT:Antu (FORS2).
		%ZTF.
  {\it Broadband photometry}:
    2MASS \citep{2006AJ....131.1163S},
    APASS \citep{2016yCat.2336....0H},
		Gaia \citep{2018A&A...616A...1G,2018A&A...616A...1G},
    SDSS \citep{2000AJ....120.1579Y},
    WISE \citep{2010AJ....140.1868W}.
}

@@

\appendix
%\section{Validation plots}
%\label{app:vetting}
%
%Figure~\ref{fig:vet} shows the type of plot used to visually assess
%whether a source was likely to be a CQV, eclipsing binary, or simply a
%rapidly rotating star.
%
%\begin{figure*}[!t]
%	\begin{center}
%    \centering
%    \includegraphics[width=0.96\textwidth]{annotated_402980664_S0018_120sec_cpvvetter.pdf}
%		\vspace{-0.45cm}
%		\caption{
%      {\bf Validation plots used to manually label CQVs}.  The complete figure
%      set, with one image per sector for each of \ncpvsfound\ CQVs
%      and candidate CQVs
%      is available online {\bf For internal collaboration review:
%      \url{https://www.dropbox.com/scl/fo/zlj3txot4cvymfb22wewu/h?dl=0&rlkey=3ec5f9o5xewrixzfkhkdenopa}}.
%      Panels are as follows.
%      {\it a)}: Phase-folded light curve; gray points are raw 2-minute
%      data and black points are binned to 200 points per cycle.
%      {\it b)}: Phase-dispersion minimization (PDM) periodogram.
%      Dotted lines show up to the 10$^{\rm th}$ harmonic and
%      subharmonic.
%      {\it c)}: DSS finder chart, with 1- and 2-TESS pixel radius
%      circles displayed for scale.
%      {\it d)}: Cleaned light curve, binned to 20-minute cadence, in
%      Barycentric TESS Julian Date (BTJD).
%      {\it e)}: Phase-folded light curve, binned to 100 points per
%      cycle.  The gray line denotes the automated spline-fit to the
%      wrapped phase-folded light curve, and small gray triangles
%      denote automatically identified local minima.
%      {\it f)}: Phase-folded light curve at twice the peak period.
%      {\it g)}: Phase-folded light curve at half the peak period.
%      {\it h)}: Phase-folded time-series within the ``background''
%      aperture defined in the SPOC light curves.
%      {\it i)}: Phase-folded flux-weighted centroid in the column
%      direction.
%      {\it j)}: Phase-folded flux-weighted centroid in the row
%      direction.
%      {\it k)}: Gaia DR2 color--absolute magnitude diagram.     
%      The gray background denotes stars within 100\,pc.
%      {\it l)}: Information from Gaia DR2, TIC8, and the automated
%      dip-counting search pipeline.  ``Neighbors'', abbreviated
%      ``nbhr'', are listed within apparent distances of 2 TESS pixels
%      if $\Delta T$$<$2.5.
%      {\it m)}: BANYAN-$\Sigma$ v1.2 association probabilities, calculated
%      using positions, proper motions, and the parallax.
%      }
%		\label{fig:vet}
%	\end{center}
%\end{figure*}

@@

\section{More neat plots}

@@

TIC~262400835 ($d$=174\,pc) is formally outside the scope of the
current work.  However, this CQV was observed using MuSCAT2 on 2020
December 12, 13, and 16, and the results are pertinent enough to the
present work.
{\bf todo: describe observations}.

>>>>

\usepackage{apjfonts}
\usepackage{url}
\usepackage{hyperref}
\usepackage{natbib}
\usepackage{amsmath,amstext,amssymb}
\usepackage[caption=false]{subfig} % for subfloat
\usepackage{xcolor, fontawesome}
\usepackage{color}
\usepackage{enumitem}

@@

%%%%%%%%%%%%%%%%
% INSTITUTIONS %
%%%%%%%%%%%%%%%%
\newcommand{\caltech}{Department of Astronomy, MC 249-17, California Institute of Technology, Pasadena, CA 91125, USA}
\newcommand{\mitkavli}{MIT Kavli Institute and Department of Physics, 77 Massachusetts Avenue, Cambridge, MA 02139}
\newcommand{\berkeley}{Astronomy Department, University of California, Berkeley, CA 94720, USA}
\newcommand{\princeton}{Department of Astrophysical Sciences, Princeton University, 4 Ivy Lane, Princeton, NJ 08540, USA}
\newcommand{\esa}{European Space Agency (ESA), European Space Research and Technology Centre (ESTEC), Keplerlaan 1, 2201 AZ Noordwijk, Netherlands}

@@

% primary authors
\author{---AUTHOR LIST \& ORDER NOT FINAL}
\author[0000-0002-0514-5538]{Luke~G.~Bouma}
\altaffiliation{51 Pegasi b Fellow}
\affiliation{\caltech}

@@

@@

\author{-----SUGGESTED CONTRIBUTORS, PENDING DISCUSSION, COMMENTS, ANALYSES, ETC-----}
%
\author{Saul~Rappaport}
\affiliation{\mitkavli}

\author[0000-0001-6381-515X]{Luisa M. Rebull}
\affiliation{\caltech}

\author[0000-0002-3164-9086]{Maximilian N. G\"unther}
\affiliation{\esa}

@@

\author[0000-0002-4265-047X]{Joshua N. Winn}
\affiliation{\princeton}

@@

% 250 word max!
\begin{abstract}
  Complex quasiperiodic variables (CQVs) are low-mass
  pre-main-sequence stars with nearly periodic optical modulation.
  The modulation is likely induced by dust or gas clumps in orbit at
  the Keplerian corotation radius.  Here, we report new CQVs
  discovered in TESS short-cadence data collected between July~2018 and Sep~2022.
  Our search of \nstarssearched\ K- and M-dwarfs with $T$$<$16 and
  $d$$<$150\,pc yielded \ngoods\ high-quality CQVs.  Most of these
  discoveries are new, and they include the brightest
  ($T$$\approx$9.5) and closest ($d$$\approx$20\,pc)
  examples of this class of object known, and perhaps the most massive
  ($\approx$0.6-0.8\,M$_\odot$).  A few objects are outliers among
  outliers; LP 12-502 for instance shows a ``dip complex'' with a
  period and total duration that are fixed over more than 1{,}000
  cycles, but which in detail exhibits anywhere from four to eight
  local minima per cycle.  LP-502 also displayed distinct superposed
  periods simultaneously, and showed drastic shape changes shortly
  after flares.  Broadly speaking, we find that none of the CQVs
  maintain a fixed light curve shape over timescales of more than a
  few hundred cycles, and we revisit the arguments for why transient
  corotating material is the most viable explanation.  In the future,
  we expect that our sample will facilitate modeling and observational
  efforts aimed at understanding these objects, and connecting them to
  the broader contexts of star, disk, and exoplanet evolution.
  For instance, if the transiting material is dust, then the rate of dip
  evolution implies that of order an asteroid belt's worth of mass
  passes through these structures over their lifetime of $10^8$ years.
\end{abstract}

@@

\begin{figure*}[!t]
	\begin{center}
		\centering
		\includegraphics[width=\textwidth]{f6.pdf}
		\vspace{-0.45cm}
		\caption{
      {\bf Properties of CQVs identified by our search}.
      The \ngoods\ bonafide CQVs in Table~\ref{tab:thetable} are 
      the black circles; \nmaybes\ candidate CQVs are gray circles.
      The top panels show the \nstarssearched\ target stars with 120-second cadence data
      as the shaded gray background;
      darker regions correspond to a larger relative number of searched stars.
      {\bf lgb todo: P vs color needs Pleiades comparison}
		}
		\label{fig:catalogscatter}
	\end{center}
\end{figure*}

@@

Based on our reading of \citet[][Ch.~8]{1992oasp.book.....G}, it seems
challenging to get neutral hydrogen to have this type of
chromaticity.  Bound-bound absorption provides opacity only at narrow
resonant lines.  Bound-free absorption can provide
wavelength-dependent opacity, but the absorption coefficients
generally {\it grow} with increasing wavelength, rather than {\it
shrink} as one needs in order to get deeper absorption in the blue
than in the red.  H$^-$  fails as a viable opacity source for the same
reason: its absorption coefficient peaks near 8500\,\AA, and is an
order of magnitude smaller at $\approx$3000\AA.
(\citealt{1992oasp.book.....G}, following \citealt{1979MNRAS.187P..59W}).
Thompson scattering is also ruled out, because it is gray.  Dust, with
its relatively featureless but increasing extinction curve when going
bluer into the optical \citep{1989ApJ...345..245C}, is to our
knowledge the most obvious opacity source.

@@

\begin{enumerate}[leftmargin=*]
	%
  \item CQVs are {\it quasi}periodic.  While the mean periods in our
    sample remain fixed over the baseline of available
    observations, the light curve shapes always evolve over timescales
    of thousands of cycles (Figure~\ref{fig:evoln}).
  %
  \item The same CQV can show dips with similar but clearly
    distinct periods.  LP 12-502, for instance, showed dips with four
    distinct periods within $\pm 0.3\%$ of its fundamental period,
    sometimes simultaneously, and each lasting for up to 50 cycles
    (Figure~\ref{fig:lpriver0}).
  %
    \item CQVs evolve over timescales that are both secular
    ($>$100\,cycles) and impulsive ($<$1 cycle).  ``State-switches''
    can cause dips to collapse instantaneously, and are often (but not
    exclusively) linked with observed optical flares.  Dip growth
    however seems to happen over durations of at least ten cycles, and
    slow dip decay also happens.
  %
    \item The rate of dip evolution can be used to place a model-dependent
    constraint on amount of material that is either being accreted or ejected
    during the state changes (Section~\ref{subsec:massflux}).
    Order of magnitude estimates require at least an asteroid belt's worth
    of dust ($10^{-4}$\,$M_\oplus$) over $10^8$ years, or 100 times more 
    material if the occulting matter is gas.
  %
    \item The CQV phenomenon persists for $\gtrsim$150\,Myr, based on
    the existence of multiple CQVs in AB Dor, the Pleiades, and
    Psc-Eri (Section~\ref{subsec:starprops}).  It may extend to even
    older ages, however the lack of detected CQVs in the Hyades and
    Praesepe suggests that the lifetime of the phenomenon may be
    limited to the first few hundred million years.
	%
    \item The duty cycle for CQVs seems to be $\approx 75$\%, based on
    the fraction of bonafide CQVs that turned on or turned off during
    TESS re-observations, two years after their initial observation.
  %
    \item While the majority of detected CQVs have masses of
    0.1-0.5\,M$_\odot$, the upper mass limit for the CQV phenomenon
    might extend into the K-dwarf regime ($<$$0.8$\,M$_\odot$).
    TIC~405754448 and TIC~405910546, with masses of $\approx$0.8 and
    $\approx$0.6 solar masses, are the two massive outliers
    (Section~\ref{subsec:extreme}), and we encourage additional
    scrutiny of these objects in future work.
  %
    \item The closest CQVs to the Sun are at distances of 15-20\,pc, and
    the brightest CQVs have $V$$\approx$12 ($J$$\approx$7.5).  This
    conclusion is an extrapolation from the CQV sample derived in this work
    being $\gtrsim$80\% complete within 20\,pc.  Expanding our analysis of
    the TESS data to the full frame images would yield a truly
    volume-limited selection function, and would expand the CQV census
    by about a factor of two within 50\,pc, and by a factor of ten
    within 100\,pc.
\end{enumerate}

@@

\facilities{
 	{\it Astrometry}:
		Gaia \citep{2018A&A...616A...1G,2022arXiv220800211G}.
 	{\it Imaging}:
    Second Generation Digitized Sky Survey. %,
    %SOAR~(HRCam; \citealt{tokovinin_ten_2018}).
		%Keck:II~(NIRC2).
		%Gemini:South~(Zorro; \citealt{scott_nessi_2018}.
		%Gemini:North~(`Alopeke; \citealt{scott_nessi_2018,scott_twin_2021}.
 	{\it Spectroscopy}:
		%CTIO1.5$\,$m~(CHIRON; \citealt{tokovinin_chironfiber_2013}),
		%PFS ({\bf CITE}),
		%Tillinghast:1.5m~(TRES).
		%MPG2.2$\,$m~(FEROS; \citealt{kaufer_commissioning_1999}),
		%AAT~(Veloce; \citealt{gilbert_veloce_2018}).
		%AAT~(HERMES; \citealt{lewis_2002_hermers_2df,sheinis_2015_hermes}),
		Keck:I~(HIRES; \citealt{1994SPIE.2198..362V}).
		%VLT:Kueyen~(FLAMES; \citealt{pasquini_2002}).
 	  %Euler1.2m~(CORALIE),
 	  %ESO:3.6m~(HARPS; \citealt{mayor_setting_2003}).
 	{\it Photometry}:
		%ASTEP:0.40$\,$m (ASTEP400),
		%CTIO:1.0m (Y4KCam),
		%Danish 1.54m Telescope,
		%El Sauce:0.356$\,$m,
		%Elizabeth 1.0m at SAAO,
		%Euler1.2m (EulerCam),
		%Kepler,
		%Magellan:Baade (MagIC),
		%Max Planck:2.2m	(GROND; \citealt{greiner_grond7-channel_2008})
		%MuSCAT3 \citep{Narita_2020},
		%NTT,
		%SOAR (SOI),
 	  TESS \citep{2015JATIS...1a4003R},
		%TRAPPIST \citep{jehin_trappist_2011},
		%VLT:Antu (FORS2).
		%ZTF.
  {\it Broadband photometry}:
    2MASS \citep{2006AJ....131.1163S},
    APASS \citep{2016yCat.2336....0H},
		Gaia \citep{2018A&A...616A...1G,2022arXiv220800211G},
    SDSS \citep{2000AJ....120.1579Y},
    WISE \citep{2010AJ....140.1868W}.
}

@@

\appendix

%\section{Validation plots}
%\label{app:vetting}
%
%Figure~\ref{fig:vet} shows the type of plot used to visually assess
%whether a source was likely to be a CQV, eclipsing binary, or simply a
%rapidly rotating star.
%
%\begin{figure*}[!t]
%	\begin{center}
%    \centering
%    \includegraphics[width=0.96\textwidth]{annotated_402980664_S0018_120sec_cpvvetter.pdf}
%		\vspace{-0.45cm}
%		\caption{
%      {\bf Validation plots used to manually label CQVs}.  The complete figure
%      set, with one image per sector for each of \ncpvsfound\ CQVs
%      and candidate CQVs
%      is available online {\bf For internal collaboration review:
%      \url{https://www.dropbox.com/scl/fo/zlj3txot4cvymfb22wewu/h?dl=0&rlkey=3ec5f9o5xewrixzfkhkdenopa}}.
%      Panels are as follows.
%      {\it a)}: Phase-folded light curve; gray points are raw 2-minute
%      data and black points are binned to 200 points per cycle.
%      {\it b)}: Phase-dispersion minimization (PDM) periodogram.
%      Dotted lines show up to the 10$^{\rm th}$ harmonic and
%      subharmonic.
%      {\it c)}: DSS finder chart, with 1- and 2-TESS pixel radius
%      circles displayed for scale.
%      {\it d)}: Cleaned light curve, binned to 20-minute cadence, in
%      Barycentric TESS Julian Date (BTJD).
%      {\it e)}: Phase-folded light curve, binned to 100 points per
%      cycle.  The gray line denotes the automated spline-fit to the
%      wrapped phase-folded light curve, and small gray triangles
%      denote automatically identified local minima.
%      {\it f)}: Phase-folded light curve at twice the peak period.
%      {\it g)}: Phase-folded light curve at half the peak period.
%      {\it h)}: Phase-folded time-series within the ``background''
%      aperture defined in the SPOC light curves.
%      {\it i)}: Phase-folded flux-weighted centroid in the column
%      direction.
%      {\it j)}: Phase-folded flux-weighted centroid in the row
%      direction.
%      {\it k)}: Gaia DR2 color--absolute magnitude diagram.     
%      The gray background denotes stars within 100\,pc.
%      {\it l)}: Information from Gaia DR2, TIC8, and the automated
%      dip-counting search pipeline.  ``Neighbors'', abbreviated
%      ``nbhr'', are listed within apparent distances of 2 TESS pixels
%      if $\Delta T$$<$2.5.
%      {\it m)}: BANYAN-$\Sigma$ v1.2 association probabilities, calculated
%      using positions, proper motions, and the parallax.
%      }
%		\label{fig:vet}
%	\end{center}
%\end{figure*}

@@

\section{More river plots}

@@

TIC~262400835 ($d$=174\,pc) is formally outside the scope of the
current work.  However, this CQV was observed using MuSCAT2 on 2020
December 12, 13, and 16, and the results might be worth including in
this study.
{\bf todo: describe observations / decide whether to include!}.
